### 2017-06-23 draft/unique-linear.tex
fine granular record permissions, take #1

Operationally, the lambda takes a deep copy of all free variables.
Thus, it must not propagate write permission to the left.
As the lambda may be invoked multiple times, the free variables must
not have write permission.
The notation $A^{X:\READ}$ means that all permissions in the types of the
variables in $X$ are set to $\READ$.
\end{document}

>>>>

Operationally, the lambda takes a deep copy of all free variables.
Thus, it must not propagate write permission to the left.
As the lambda may be invoked multiple times, the free variables must
not have write permission.
The notation $A^{X:\READ}$ means that all permissions in the types of the
variables in $X$ are set to $\READ$.

\section{Third Attempt: Field Effects}
\label{sec:third-attempt:-field}

\begin{mathpar}
  \inferrule{
    A = A_1 \OVERRIDE \dots \OVERRIDE A_n \\
    A_i \vdash e_i : t_i 
  }{
    A \vdash \REC{ \overline{a_i=e_i}} : \REC{ \overline{a_i : t_i}}
  }
\end{mathpar}

\begin{mathpar}
  \inferrule
  {
    A \vdash e : \REC{ a:^\READ t \mid r}
    % \\ \READ \in P
  }
  {
    A \vdash \GET ea : t
  }
\end{mathpar}

\begin{mathpar}
  \inferrule{
    A_0 \vdash e_0 : \REC{ a:^\WRITE t \mid r} \\
    A_1 \vdash e_1 : t \\
    % \WRITE \in P \\
    A = A_0 \OVERRIDE A_1
  }{
    A \vdash \UPD {e_0}a{e_1} : \REC{ a:t \mid r}
  }
\end{mathpar}

\begin{mathpar}
  \inferrule{
  }{
    A, x: t \vdash x:t
  }
\end{mathpar}

Look at combining $a :^O t \OVERRIDE a:^P t$ upwards to $a : ^Q t$
\begin{itemize}
\item $O\subseteq \{\READ\}$: $Q = O \cup P$,
  no further action required as potential writing in $P$ happens after reading
\item $\WRITE \in O$, $P \subseteq \{\READ\}$: two choices, not clear
  which is better
  \begin{itemize}
  \item $Q = \READ$ insert copy, propagate left to the write operation
  \item $Q = \WRITE$ insert copy, propagate right to the read operation
  \end{itemize}
\item $\WRITE\in O$, $\WRITE \in P$: $Q = \WRITE$ insert copy,
  propagate left (or right)
\end{itemize}

\begin{mathpar}
  \inferrule
  { A \vdash e_1 : t_1 \\
    A, x : t_1 \vdash e_2 : t_2
  }
  { A \vdash \LET x{e_1} e_2 : t}
\end{mathpar}

\end{document}
